---
title: "Analysis of Amazon Stiller Task Data"
author: "Martin Fortier, Danielle Kellier, and Mike Frank"
date: '`r Sys.Date()`'
output:
  html_document:
  toc: yes
highlight: tango
theme: spacelab
---

This report covers 2017 data collection.

The script has been revised in response to reviewer comments in Winter 2023. 

# Data prep

Libraries. 

```{r}
library(tidyverse)
library(langcog) # github.com/langcog/langcog
library(lme4)
library(brms)
library(knitr)
library(BayesFactor)
library(ggthemes)
theme_set(theme_few())
```

Read sheets. 

```{r}
raw_data <- read_csv("data/amazon_pragmatics_data.csv")
orders <- read_csv("data/amazon_pragmatics_orders.csv")
```

Now merge in stimulus information. 

Note, we previously excluded children > 10 years old. Now we leave them in. 

```{r}
d_raw <- raw_data |>
  mutate(Subid = 1:n()) |>
  rename(Order = Orden, 
         Gender = Genero) |>
  gather(Trial, Choice, `Trial 1`:`Trial 10`) |>
  mutate(Trial = as.numeric(str_sub(Trial,start = -2, -1))) |>
  left_join(orders) |>
  rename(TrialType = `Trial Type`) |>
  mutate(Correct = Choice == Target, 
         TargetStimulus = ifelse(Target == "L", L, R)) |>
  select(Subid, Age, Gender, Order, Trial, Choice, Target, TrialType, Stimulus, TargetStimulus, Correct) |>
  mutate(age_grp = case_when(
    Age > 4 & Age <= 6 ~ "4 - 6",
    Age > 6 & Age <= 8 ~ "6 - 8",
    Age > 8  ~ "8+"),
    TrialType = fct_recode(TrialType, 
                           `Control-Double` = "ControlDouble",
                           `Control-Single` = "ControlSingle",
                           `Warm-Up` = "Warm-up",
                           `Pragmatic Inference` = "Test")) 

```



```{r}
subs <- d_raw |>
  group_by(Subid, age_grp) |>
  summarise(Age = Age[1], 
            n_trials = sum(!is.na(Correct)), 
            correct = mean(Correct), 
            gender = Gender[1]) 

ggplot(subs, aes(x = Age)) + 
  geom_histogram(binwidth = .5, center = 0) 
```


```{r}
subs |>
  group_by(age_grp) |>
  summarise(mean_age = mean(Age, na.rm=TRUE),
            sd_age = sd(Age, na.rm=TRUE),
            max_age = max(Age, na.rm=TRUE), 
            min_age = min(Age, na.rm=TRUE),
            n_trials = mean(n_trials), 
            n = n(), 
            missing_age = sum(is.na(Age)), 
            n_male = sum(gender == "M"), 
            prop_male = n_male / n) |>
  kable(digits = 2)

```
# Primary analysis

Start by filtering missing ages.

```{r}
d <- d_raw |>
  mutate(TrialType = fct_relevel(TrialType, "Pragmatic Inference")) |>
  filter(!is.na(Age))
```

Now let's make the primary plot. 

```{r}
mbs <- d |>
  group_by(TrialType, Age, age_grp, Subid) |>
  summarise(Correct = mean(Correct, na.rm=TRUE),
            n = n())

ms <- mbs |>
  group_by(TrialType, age_grp) |>
  langcog::multi_boot_standard(col = "Correct", na.rm=TRUE) |>
  mutate(Age = case_when(age_grp == "4 - 6" ~ 5,
                         age_grp == "6 - 8" ~ 7,
                         age_grp == "8+" ~ 9))

ggplot(mbs,
       aes(x = Age, y = Correct, 
           col = TrialType, shape = TrialType)) + 
  geom_jitter(width = 0, height = .05, alpha = .5) +
  geom_pointrange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .05)) + 
  geom_line(data = filter(ms, age_grp != "exclude"), 
            aes(y = mean, group = TrialType)) + 
  geom_hline(lty = 2, yintercept = .5) + 
  scale_color_colorblind(name = "Trial Type" ) + 
  scale_shape_few(name = "Trial Type" ) + 
  ylab("Proportion Correct") + 
  xlab("Age Group (years)") + 
  theme(legend.position = "bottom")
```

And by items.

```{r}
mbs_items <- d |>
  filter(TrialType %in% c("Pragmatic Inference", 
                          "Control-Double")) |>
  group_by(TrialType, Age, age_grp, Stimulus, Subid) |>
  summarise(Correct = mean(Correct, na.rm=TRUE),
            n = n())

ms_items <- mbs_items |>
  group_by(TrialType, Stimulus, age_grp) |>
  langcog::multi_boot_standard(col = "Correct", na.rm=TRUE) 

ggplot(mbs_items,
       aes(x = age_grp, y = Correct, 
           col = TrialType, shape = TrialType)) + 
  geom_pointrange(data = ms_items, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .05)) + 
  geom_line(data = ms_items, 
            aes(y = mean, group = TrialType)) + 
  geom_hline(lty = 2, yintercept = .5) + 
  scale_color_manual(name = "Trial Type",
                         values = c("Pragmatic Inference" = "#000000", 
                                    "Control-Double" = "#E69F00") ) + 
  scale_shape_few(name = "Trial Type" ) + 
  ylab("Proportion Correct") + 
  xlab("Age Group (years)") + 
  theme(legend.position = "bottom") + 
  facet_wrap(~Stimulus)
```


# Stats

## Model

Maximal random effects structure. Note that this model is no longer included in the manuscript for reasons of parsimony. 

```{r eval=FALSE}
bayes_mod <- brm(as.numeric(Correct) ~ TrialType * scale(Age) 
                 + (TrialType | Subid) 
                 + (TrialType * scale(Age) | Stimulus), 
                 family = "bernoulli", 
                 data = filter(d, age_grp != "exclude"))
kable(fixef(bayes_mod), digits = 2)
```

## Bayesian hypothesis tests

Control-single all kids. 

```{r}
ttestBF(filter(mbs,TrialType=="Control-Single")$Correct, mu = .5)
```

Control-single by age.

```{r}
ttestBF(filter(mbs,TrialType=="Control-Single" & age_grp == "4 - 6")$Correct, mu = .5)
ttestBF(filter(mbs,TrialType=="Control-Single" & age_grp == "6 - 8")$Correct, mu = .5)
ttestBF(filter(mbs,TrialType=="Control-Single" & age_grp == "8+")$Correct, mu = .5)
```

Inference trials. 

```{r}
ttestBF(filter(mbs, TrialType=="Pragmatic Inference")$Correct, mu = .5)
```

By age.

```{r}
ttestBF(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "4 - 6")$Correct, mu = .5)

ttestBF(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "6 - 8")$Correct, mu = .5)

ttestBF(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "8+")$Correct, mu = .5)
```

## Frequentist t-tests

Control-single all kids. 

```{r}
t.test(filter(mbs,TrialType=="Control-Single")$Correct- .5)
```

By age.

```{r}
t.test(filter(mbs,TrialType=="Control-Single" & age_grp == "4 - 6")$Correct - .5)
t.test(filter(mbs,TrialType=="Control-Single" & age_grp == "6 - 8")$Correct - .5)
t.test(filter(mbs,TrialType=="Control-Single" & age_grp == "8+")$Correct - .5)
```

Inference trials. 

```{r}
t.test(filter(mbs, TrialType=="Pragmatic Inference")$Correct - .5)
```

By age.

```{r}
t.test(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "4 - 6")$Correct - .5)

t.test(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "6 - 8")$Correct - .5)

t.test(filter(mbs,TrialType=="Pragmatic Inference" & age_grp == "8+")$Correct - .5)
```

# Side bias 

Look at side biase effects. Not any huge evidence of side bias, though overall test performance higher when target is on the R.

```{r}
mbs_side <- d |>
  group_by(TrialType, Target, Subid) |>
  summarise(Correct = mean(Correct, na.rm=TRUE),
            n = n())

ms_side <- mbs_side |>
  group_by(TrialType, Target) |>
  langcog::multi_boot_standard(col = "Correct", na.rm=TRUE) 


ggplot(mbs_side, aes(x = Target, y = Correct, col = TrialType)) + 
  geom_pointrange(data = ms_side, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .05)) + 
  geom_hline(lty = 2, yintercept = .5) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


