---
title: "Analysis of Amazon Stiller Task Data"
author: "Martin Fortier, Danielle Kellier, and Mike Frank"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
  html_notebook:
    code_folding: hide
    highlight: tango
    theme: spacelab
    toc: yes
---

Note that this report only covers "V2" of the experiment. 

# Data prep

Libraries. 

```{r}
library(readxl)
library(tidyverse)
library(langcog)
theme_set(theme_bw())
```

Read sheets. 

```{r}
raw_data <- read_excel("data/summer2016-v2.xlsx", sheet = 1)
slide_info <- read_excel("data/summer2016-v2.xlsx", sheet = 2)
targets <- read_excel("data/summer2016-v2.xlsx", sheet = 3)
```

Now merge in stimulus information. 

```{r}
df <- raw_data %>%
  mutate(subid = factor(paste0(as.character(id), "-",
                        as.character(date)))) %>%
  gather(stimulus, choice, sacha_vaca:mototaxi) %>%
  left_join(rename(slide_info, choice = code)) %>%
  left_join(targets) %>%
  mutate(correct = choice == target_code) %>%
  select(-id) 
```

# Primary analysis 

Now get grand means.

```{r}
mbs <- df %>%
  group_by(trial_type, subid) %>%
  summarise(correct = mean(correct, na.rm=TRUE),
            n = n())

ms <- mbs %>%
  group_by(trial_type) %>%
  multi_boot_standard(col = "correct")

ggplot(mbs, aes(x = trial_type, y = correct)) + 
  geom_jitter(width = .05, height = .05) + 
  geom_pointrange(col = "red", data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(lty = 2, yintercept = .33)
```

Performance is low. Check for developmental trends. Only older kids perform even above chance on control trials. 

```{r}
mbs <- df %>%
  group_by(trial_type, age, subid) %>%
  summarise(correct = mean(correct, na.rm=TRUE),
            n = n())

ms <- mbs %>%
  group_by(trial_type, age) %>%
  multi_boot_standard(col = "correct")

ggplot(mbs, aes(x = age, y = correct, col = trial_type)) + 
  geom_jitter(width = .05, height = .05) + 
  geom_linerange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                 position = position_dodge(width = .05)) + 
  geom_line(data = ms, 
                  aes(y = mean)) + 
  geom_hline(lty = 2, yintercept = .33) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1)
```

# Sub analyses - items and items/age

Look at item effects. 

```{r}
mbs <- df %>%
  group_by(trial_type, stimulus, subid) %>%
  summarise(correct = mean(correct, na.rm=TRUE),
            n = n())

ms <- mbs %>%
  group_by(trial_type, stimulus) %>%
  multi_boot_standard(col = "correct", na.rm=TRUE)

ggplot(mbs, aes(x = stimulus, y = correct, col = trial_type)) + 
  geom_pointrange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                 position = position_dodge(width = .05)) + 
  geom_line(data = ms, 
                  aes(y = mean)) + 
  geom_hline(lty = 2, yintercept = .33) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1)
```

And cross with age?

```{r}
mbs <- df %>%
  group_by(trial_type, age, stimulus, subid) %>%
  summarise(correct = mean(correct, na.rm=TRUE),
            n = n())

ms <- mbs %>%
  group_by(trial_type, age, stimulus) %>%
  multi_boot_standard(col = "correct", na.rm=TRUE)

ggplot(mbs, aes(x = age, y = correct, col = trial_type)) + 
  facet_wrap(~stimulus) + 
  geom_pointrange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                 position = position_dodge(width = .05)) + 
  geom_line(data = ms, 
                  aes(y = mean)) + 
  geom_hline(lty = 2, yintercept = .33) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1)
```

# Site analysis


```{r}
mbs <- df %>%
  group_by(trial_type, age, location, subid) %>%
  summarise(correct = mean(correct, na.rm=TRUE),
            n = n())

ms <- mbs %>%
  group_by(trial_type, age, location) %>%
  multi_boot_standard(col = "correct", na.rm=TRUE)

ggplot(mbs, aes(x = age, y = correct, col = trial_type)) + 
  facet_wrap(~location) + 
  geom_pointrange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                 position = position_dodge(width = .05)) + 
  geom_line(data = ms, 
                  aes(y = mean)) + 
  geom_hline(lty = 2, yintercept = .33) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1)
```

# Choice distribution

Examine distribution of choices, rather than correctness.

It appears that most kids (at least until age 6) are not understanding the task much, but they do choose "both" slightly more than target. But they are also pretty close to chance. 

```{r}
mbs <- df %>%
  filter(trial_type == "inference") %>%
  group_by(age, subid, item_type) %>%
  summarise(n = n()) %>%
  group_by(age, subid) %>%
  mutate(prop = n / sum(n), 
         item_type = factor(item_type)) %>%
  complete(item_type, nesting(subid), fill = list(prop = 0))

ms <- mbs %>%
  group_by(age, item_type) %>%
  multi_boot_standard(col = "prop", na.rm=TRUE)

ggplot(mbs, aes(x = age, y = prop, col = item_type)) + 
  geom_pointrange(data = ms, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                 position = position_dodge(width = .05)) + 
  geom_line(data = ms, 
                  aes(y = mean)) + 
  geom_hline(lty = 2, yintercept = .33) + 
  scale_color_solarized() + 
  ylab("Proportion correct") + 
  xlab("Age (years)") + 
  ylim(0,1)
```

